Given a manifold $M$, a \textit{Ricci Flow} is a smooth family $g(t)$, with $ t \in [0,T)$, of Riemannian metrics satisfying the evolution equation

\begin{equation}\label{eq1}
    \partial_t g(t) = -2 Ric_{g(t)}
\end{equation}
where $Ric_{g(t)}$ is the Ricci tensor for the metric $g(t)$, i.e. the contraction of the Riemann tensor obtained with $g(t)$; in components $Ric_{g(t)}^{ij} \equiv g_{kl}(t)R^{iklj}$ \cite{recentdevelopmentsricciflows}.

The metric is deformed in a way which smooths out its irregularities, like in a heat diffusion process. Indeed, using harmonic local coordinates, the Ricci tensor approximates the Laplacian\footnote{Actually the operator $\triangle$ in Equation \hyperref[eq2]{2} is the Laplace-Beltrami operator, a generalization of the Laplace operator to functions defined on Riemannian and pseudo-Riemannian manifolds.} of the metric up to lower-order terms in derivatives of the metric tensor:
\begin{equation}\label{eq2}
    Ric_{g} = -\frac{1}{2}\triangle g + \textit{lower-order terms}
\end{equation}
which plugged into Equation \hyperref[eq1]{1} results in a nonlinear heat equation \cite{theRicciFlowAnIntroduction}.

By viewing a network as a discrete analogue of a 3-manifold, we can interpret the process of community detection as a geometric decomposition analogous to how Ricci Flow decomposes a 3-manifold into distinct geometric regions. Each community in the network represents a cohesive region of the network, much like a geometric region in a manifold. 
Inter-community edges are analogous to the boundaries between geometric regions in the manifold while intra-community edges represent connections within a homogeneous geometric region.


\section{Ollivier's Ricci Curvature}

Ollivier's Ricci curvature is a discrete adaptation of the classical Ricci curvature defined for smooth manifolds, tailored for graph structures. In a network, nodes represent points, and edges between them denote "distances" or connections. Rather than relying on continuous geometry, Ollivier's Ricci curvature measures how well-connected neighboring nodes are by comparing the distances between their neighborhoods.

In a graph, each node $x$ has a set of neighboring nodes, and we assign a probability distribution over this set, denoted as $m_x$. This distribution can be thought of as how much "mass" each neighbor carries. For example, the nodes $x$ and $y$ in Figure \hyperref[fig1]{1} each have three neighbors, and the respective probability distributions over their neighborhoods are denoted as $m_x$ and $m_y$.

\begin{figure} \label{fig1}
    \centering
    \begin{tikzpicture}
        % Nodes for x and its neighbors
        \node[draw, circle, fill=blue!20] (x) at (0, 0) {$x$};
        \node[draw, circle] (a) at (-1.5, 1.5) {$a$};
        \node[draw, circle] (b) at (-2, 0) {$b$};
        \node[draw, circle] (c) at (-1.5, -1.5) {$c$};
        
        % Nodes for y and its neighbors
        \node[draw, circle, fill=green!20] (y) at (4, 0) {$y$};
        \node[draw, circle] (d) at (5.5, 1.5) {$d$};
        \node[draw, circle] (e) at (6, 0) {$e$};
        \node[draw, circle] (f) at (5.5, -1.5) {$f$};
        
        % Edges connecting x and its neighbors
        \draw[thick] (x) -- (a) node[midway, above, sloped] {\footnotesize 0.5};
        \draw[thick] (x) -- (b) node[midway, below] {\footnotesize 0.3};
        \draw[thick] (x) -- (c) node[midway, below, sloped] {\footnotesize 0.2};
        
        % Edges connecting y and its neighbors
        \draw[thick] (y) -- (d) node[midway, above, sloped] {\footnotesize 0.4};
        \draw[thick] (y) -- (e) node[midway, below] {\footnotesize 0.4};
        \draw[thick] (y) -- (f) node[midway, below, sloped] {\footnotesize 0.2};
        
        % Edge between x and y
        \draw[thick, dashed] (x) -- (y) node[midway, above] {$d(x, y)$};
    \end{tikzpicture}
    \caption{Nodes $x$ and $y$ with their respective neighborhoods and probability distributions. The weights on the edges represent the probability distribution $m_x$ for node $x$'s neighbors and $m_y$ for node $y$'s neighbors.}
\end{figure}



Formally, the Ollivier-Ricci curvature $\kappa(x, y)$ between two connected nodes $x$ and $y$ is defined using the \textit{earthmover's distance}, also known as the \textit{Wasserstein distance}, between probability distributions on the neighborhoods of $x$ and $y$:
\begin{equation}\label{eq3}
    \kappa(x, y) = 1 - \frac{W_1(m_x, m_y)}{d(x, y)}
\end{equation}
where
\begin{itemize}
    \item $d(x, y)$ is the shortest path distance between nodes $x$ and $y$.
    \item $W_1(m_x, m_y)$ is the Wasserstein-1 distance between the probability distributions of neighboring nodes around $x$ and $y$:
    \begin{equation}
        W_1(m_x, m_y) = \textit{inf} \left\{ \left. \int\limits_{X \times Y} d(x,y) d\gamma(x,y) \right| \gamma \in \Gamma(m_x, m_y)  \right\}
    \end{equation}
    with $\gamma$ being a probability measure on $X \times Y$ (the probability spaces of the neighboring nodes around $x$ and $y$) and $\Gamma(m_x, m_y)$ indicating the collection of all possible transportation plans.
\end{itemize}

This curvature provides a natural way to quantify the coupling between two neighborhoods. High positive curvature implies that the neighborhoods of $x$ and $y$ are tightly connected, whereas negative curvature indicates sparse or loosely connected regions \cite{communitydetectionnetworksricci}.

Edges with high positive curvature tend to represent intra-community connections, while edges with low or negative curvature correspond to inter-community links. This distinction allows us to leverage geometric intuition for community detection, adjusting edge weights based on their curvature values.




\section{The Discrete Ricci Flow Algorithm}
The discrete Ricci flow algorithm modifies the concept of Ricci Flow to suit network structures by iteratively updating the weights of the edges according to their curvature values. The steps of the algorithm are as follows:

\begin{enumerate}
    \item \textbf{Initialization}: Begin with a graph $G(V, E)$, where $V$ is the set of vertices and $E$ is the set of edges. Each edge $(x, y) \in E$ is assigned an initial weight, which can be based on the shortest path distance between nodes $x$ and $y$, or on a predefined edge weight.
    
    \item \textbf{Curvature Computation}: For each edge $(x, y)$, compute the Ollivier-Ricci curvature $\kappa(x, y)$. The Wasserstein distance here is defined as the minimum total weighted travel distance to move $m_x$ to $m_y$, i.e.
    \begin{equation}
        W(m_x,m_y) =  \textit{inf} \left\{ \sum\limits_{u,v\in V} A(u,v) d(u,v)  \right\}
    \end{equation}
    where $A(u,v)$ is a map $V\times V \rightarrow [0,1]$ called \textit{discrete transport plan}. It corresponds to the amount of mass moved from vertex $u \in V_x$ (a neighbor of $x$) to vertex $v \in V_y$ (a neighbor of $y$). The transport plan satisfies $\sum_{v \in V} A(u,v) = m_x(u)$ and $\sum_{u \in V} A(u, v) = m_y(v)$, where $m_x (u)$ and $m_y(v)$ are the probability distributions on the neighborhoods of $x$ and $y$ respectively. These conditions ensure that the total mass leaving node $x$ matches the distribution $m_x$, and the total mass arriving at node $y$ matches $m_y$.
    \item \textbf{Edge Weight Update}: Modify the weights of the edges based on their curvature values. If $\kappa(x, y)$ is positive, reduce the edge weight, simulating a contraction of intra-community edges. Conversely, if $\kappa(x, y)$ is negative, increase the edge weight, stretching inter-community edges. The updated weight $w'(x, y)$ is given by:
    \begin{equation}\label{eq4}
    w'(x, y) = w(x, y) \times (1 - \alpha \cdot \kappa(x, y))
    \end{equation}
    where $\alpha$ is a step size parameter controlling the rate of change.
    
    \item \textbf{Iteration}: Repeat the process of computing curvature and updating edge weights for a specified number of iterations or until convergence is achieved. Over time, intra-community edges shrink (strengthen) while inter-community edges stretch (weaken), causing communities to become more distinct.

    \item \textbf{Surgery Process}: Remove edges that contribute to singularities. Edges with a curvature value below a certain threshold, typically set $\approx -0.1$, are pruned. It is worth mentioning that there are other techniques to modify the graph structure to deal with problematic regions, effectively 'surgically' altering the graph to maintain the flow's stability. Common ones are edge contraction (i.e. reducing the weight of edges that are causing high curvature) and node splitting (i.e. dividing a single node into multiple nodes while redistributing the connected edges among them).
    

    \item \textbf{Community detection}: After the edge weights have been updated through the Ricci Flow iterations, we apply the Louvain method for community detection, which returns a partition of the network based on the modified edge weights from the Ricci Flow process, where each node is assigned to a community.  
\end{enumerate}



\section{Convergence Criteria and Stopping Conditions} \label{sec2.3}
The theoretical foundation of the discrete Ricci Flow method for community detection is supported by several key results, one of the most important being the convergence guarantees provided by Theorem 4.1 from \cite{communitydetectionnetworksricci}.

%\begin{theorem}[Theorem 4.1, \cite{communitydetectionnetworksricci}] \label{th1}
\color{red}THEOREM\color{black}
The Ricci flow associated with the Ollivier $K_0$-Ricci curvature \footnote{$K_0$-Ricci curvature is a modification of Ollivier-Ricci curvature which incorporates a parameter $K_0$ in order to adjust the curvature calculation; emphasizing certain aspects of community structure.} detects the community structure on $G(a, b)$ if $a > b \geq 2$. Specifically, the algorithm asymptotically shrinks the weights of intra-community edges faster than the weights of inter-community edges. %This process effectively partitions the graph $G(a, b)$ into distinct communities.
%\end{theorem}

Theorem \hyperref[th1]{1} guarantees the convergence of the discrete Ricci Flow algorithm, meaning that after a finite number of iterations, the edge weights stabilize and no further significant changes occur. This convergence ensures that the community structure revealed by the Ricci Flow process is robust and does not depend on further iterations.

While Ricci Flow has inherent convergence properties that can lead to well-separated communities, some practical stopping conditions will often be required for implementation:

\begin{enumerate}
    \item \textbf{Change in Edge Weights}: 
    Monitor the change in edge weights between iterations. Convergence is achieved when the change falls below a predefined threshold $\epsilon$, indicating that the algorithm has stabilized:
    \[
    \max_{(x, y) \in E} |w_{\text{new}}(x, y) - w_{\text{old}}(x, y)| < \epsilon
    \]
    
    \item \textbf{Community Structure Stability}: 
    Validate the stability of the detected community structure across iterations. Ensure that identified communities remain consistent and meaningful by assessing their internal cohesion and external separation.
    
    \item \textbf{Maximum Iterations}: 
    Define a maximum number of iterations $N_{\text{max}}$ to prevent excessive computation and to facilitate early stopping if convergence is not achieved within this limit:
    \[
    \text{If } k > N_{\text{max}}, \text{ stop algorithm}
    \]
\end{enumerate}
